Aneuploidy can be an evolutionary detour \\ on the path to adaptation

### 2023-11-23 ms/ms.tex
submit to mbe

% Acknowledgements
{\small
\section*{Acknowledgements}
We thank Lilach Hadany, Judith Berman, David Gresham, Shay Covo, Martin Kupiec, Anna Selmecki, Petra Vande Zande, Uri Obolski, Daniel Weissman, and Tal Simon for discussions and comments.
This work was supported in part by 
the Israel Science Foundation~(ISF, YR 552/19),
the US--Israel Binational Science Foundation~(BSF, YR 2021276),
Minerva Center for Live Emulation of Evolution in the Lab~(YR, YP),
Minerva Stiftung short-term research grant~(MP).
}

>>>>

% Acknowledgements
{\small
\section*{Acknowledgements}
We thank Lilach Hadany, Judith Berman, David Gresham, Shay Covo, Martin Kupiec, Uri Obolski, Daniel Weissman, and Tal Simon for discussions and comments.
This work was supported in part by 
the Israel Science Foundation~(ISF, YR 552/19),
the US--Israel Binational Science Foundation~(BSF, YR 2021276),
Minerva Center for Live Emulation of Evolution in the Lab~(YR, YP),
Minerva Stiftung short-term research grant~(MP).
}
